Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Changed order of figures in figure 10
Fritz's problem is not stated ambiguously

    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to rigorously compare the qualitative features of differing non-classical distributions on differing causal structures (such as the Bell and Triangle structures). The remainder of this paper focuses on our advancement toward solving Fritz's Problem. \Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.

@@

    \begin{definition}
        \label{def:inflation}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
    \end{definition}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{center}
    For each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index. For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}. Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).

>>>>

    Fritz's problem is concerned with how to find and recognize non-classical quantum distributions specifically for the Triangle structure. In \cite{Fritz_2012}, Fritz proves the Fritz distribution is non-classical by \textit{recycling} Bell's theorem. Being limited by the requirement of perfect correlations and the reliant on Bell's theorem, Fritz's methods are problematic if one hopes to find new quantum resources for the Triangle structure. The remainder of this paper focuses on our advancement toward solving Fritz's Problem. \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem. Afterwards, \Cref{sec:found_inequalities} reports the discovery of new causal compatibility inequalities wish are capable of proving the non-classicality of Fritz's distribution. Finally, \Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.

@@

    \begin{definition}
        \label{def:inflation}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
    \end{definition}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
    \end{subfigure}
    \begin{subfigure}[b]{.30\linewidth}
    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
    \caption{The Web Inflation.}\label{fig:the_web_inflation}
    \end{subfigure}
    \caption{Some inflations of the Triangle structure.}
    \label{fig:inflations}
    \end{figure}
    \end{center}
    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
    \end{subfigure}
    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
    \end{subfigure}
    \begin{subfigure}[b]{.23\linewidth}
    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
    \end{subfigure}
    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
    \label{fig:injectablesets}
    \end{figure}
    \end{center}
    For each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index. For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}. Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).
